\cvsection{Experience}
\begin{cventries}
\nopagebreak

% Example entry:
% \cventry
%   {Your Position}
%   {Company Name}
%   {Location}
%   {Start Date~-~End Date}
%   {\begin{cvitems}
%     \item {Description of your key responsibilities and achievements}
%     \item {Technologies and methodologies used}
%     \item {Impact and results of your work}
%   \end{cvitems}}

\cventry
  {Orchestration Engineer} % Job title
  {NOS SGPS} % Organization
  {Lisbon, Portugal} % Location
  {Apr. 2024~-~Present} % Date(s)
  {
    \begin{cvitems}
      \item {Led technical initiatives to modernize \textbf{datacenter automation} through workflow orchestration, replacing legacy systems with a scalable, \textbf{cloud-native architecture} enabling future automation capabilities.}
      \item {Drove the adoption of \textbf{Camunda} within a \textbf{Kubernetes} environment as the central orchestration engine, establishing a platform designed for extensibility and separation of concerns.}
      \item {Engineered a comprehensive \textbf{CI/CD} pipeline for \textbf{BPMN} processes, enabling automated deployment, testing, and validation of workflow definitions.}
      \item {Architected \textbf{TMForum-compliant} service and resource catalogs and order management system, establishing a modular architecture that integrates with existing enterprise systems through \textbf{standardized APIs}.}
      % \item {Skills: Problem-solving, Critical Thinking, Camunda, Kubernetes, CI/CD, BPMN, API Integration, TMForum, Service Catalogs, Order Management Systems}
    \end{cvitems}
  }

%---------------------------------------------------------

\cventry
  {Systems Engineer (Infrastructure Team)} % Job title
  {} % Organization
  {} % Location
  {Oct. 2023~-~Apr. 2024} % Date(s)
  {
    \begin{cvitems}
      \item {Gathered scattered data on the total amount of storage capacity available and developed a \textbf{PowerBI} dashboard for real-time monitoring}
      \item {Led the migration of the \textbf{SAN} switches that supported laboratory infrastructure}
      % \item {Skills: SAN, Storage, Virtualization, VMware}
    \end{cvitems}
  }

\vspace{1mm}

%---------------------------------------------------------
\cventry
  {IT Systems Manager} % Job title
  {World Youth Day Lisbon 2023} % Organization
  {Lisbon, Portugal} % Location
  {Jan. 2023~-~Aug. 2023} % Date(s)
  {
    \begin{cvitems}
      \item {Led the Volunteer IT Systems team, overseeing the planning, development, and deployment of IT solutions to support event operations}
      \item {Guaranteed data quality and integrity between \textbf{4 systems} using \textbf{Python} scripts}
      \item {Optimized the assignment of \textbf{25k volunteers} through a \textbf{Python} algorithm to automatically generate teams' schedule}
      \item {Implemented a \textbf{PowerBI} dashboard to make the volunteer data easily accessible in help desks during the event}
      % \item {Skills: Microsoft Excel, Python, Data Analysis, Communication, Leadership, Project Management}
    \end{cvitems}
  }
  
%---------------------------------------------------------

% \cventry
%   {U@Deloitte Virtual Summer Edition Intern} % Job title
%   {Deloitte} % Organization
%   {Lisbon, Portugal} % Location
%   {Jul. 2020~-~Jul. 2020} % Date(s)
%   {
%     \begin{cvitems}
%       \item {Intern in the Network Security Knowledge Lake of the Telecom Engineering Centre of Excellence team.}
%       \item {Worked on a project about Cloud Security and learned Deloitte's culture}
%       \item {Skills: Cloud Security, Microsoft PowerPoint, Adaptability, Teamwork}
%     \end{cvitems}
%   }
  
%---------------------------------------------------------

\end{cventries}
